The \dealii Library, Version 9.6

### 2024-08-19 9.6/paper.tex
remove authors from contributors

 \author[1*]{Pasquale~Claudio~Africa}
 \affil[1]{SISSA International School for Advanced Studies,
   mathLab,
   Via Bonomea, 265,
   34136, Trieste, Italy.
   \texttt{pafrica@sissa.it}}

@@

\dealii version 9.6.0 was released August 11, 2024.
This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii software library version 9.6. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL). Downloads are available at
\url{https://www.dealii.org/} and \url{https://github.com/dealii/dealii}.

@@

The 9.6 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_5_2_and_9_6_0.html}
     {around X incompatible changes};
see \cite{changes96}. Many of these
incompatibilities change internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
  \item CUDAWrappers, that enable the usage of cuSPARSE algorithms, have been deprecated and will be removed in the next release. Kokkos is now used for device-specific optimizations.
\end{itemize}

>>>>

 \author[1*]{Pasquale~Claudio~Africa}
 \affil[1]{SISSA International School for Advanced Studies,
   mathLab,
   Via Bonomea, 265,
   34136O, Trieste, Italy.
   \texttt{pafrica@sissa.it}}

@@

\dealii version 9.6.0 was released X X, 2024.
This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii software library version 9.6. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL). Downloads are available at
\url{https://www.dealii.org/} and \url{https://github.com/dealii/dealii}.

@@

The 9.6 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_5_2_and_9_6_0.html}
     {around X incompatible changes};
see \cite{changes96}. Many of these
incompatibilities change internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
  \item CUDAWrappers
\end{itemize}
